---
title: "Endsem"
author: "Shubhang Periwal 19201104"
date: "11/28/2019"
output: pdf_document
---

```{r }
setwd("D:/rprog")
library(ggplot2)
library(rio)
library(tidyverse)
library(plotly)
library(gganimate)
library(inline)
library(pixmap)
library(MASS)
library(dplyr)
```

## R Markdown

question 1
```{r }
ds1 <- import("HR021.csv",setclass = "tibble",header=TRUE)
ds2 = import("s50_1997.txt")
ds3 = import("s50_1995.txt")
ds2
ds3
```


Question 2
```{r }
#a
ds3$alcohol = factor(ds3$alcohol)
ds3$drugs = factor(ds3$drugs)
ds3$smoke = factor(ds3$smoke)
ds3$sport = factor(ds3$sport)
str(ds3)
```




```{r }
#Q2 b
#,legend("topright",legend=c("Not","Occasional","Regular"),lty=c(1,1,1),lwd = c(3,3,3),col=c("green","blue","red"))

t1 = table(ds3$smoke)
t2 = table(ds3$sport)
x = barplot(t1,xlab="Frequency of Smoking",ylab="Number of People",ylim = c(0,50),col=c("green","blue","red"))
y =  barplot(t2,xlab="Frequency of Playing",ylab="Number of People",ylim = c(0,50),col=c("blue","red"))

par(mfrow=c(1,2))
x
y
```
The resulting plots show that there are high number of non smokers and low number of actual smokers, 
which is a good thing. 
The number of students who play regularly are almost 3 times the number of people who do not play. 
This shows that there maybe a positive correlation between students who play and students who 
don't smoke. 
```{r }
#c

y2 = length(ds3$smoke)
y1 = length(which(ds3$smoke=="3")) + length(which(ds3$smoke=="2"))
y1/y2

y3 = length(which(ds3$smoke=="3" & ds3$sport=="2")) + length(which(ds3$smoke=="2" & ds3$sport=="2"))
y3/y2
```
The proportion of pupils who smoke atleast occassionaly is 0.24
The proportion of pupils who smoke and play is 0.18

```{r }
#d
class(ds3) <- c("s50survey")
summary.s50survey <- function(ds3){
  l1 = length(ds3$smoke)
  l2 = length(ds3$drugs)
  l3 = length(ds3$alcohol)
  l4 = length(ds3$sport)
  
  hsm = length(which(ds3$smoke=="3"))/l1
  lsm = length(which(ds3$smoke=="2"))/l1
  nsm = length(which(ds3$smoke=="1"))/l1
  
    hd = length(which(ds3$drugs=="4"))/l2
  ld = length(which(ds3$drugs=="2"))/l2
  nd = length(which(ds3$drugs=="1"))/l2
  md = length(which(ds3$drugs=="3"))/l2
  
  al1 = length(which(ds3$alcohol=="1"))/l3
  al2 = length(which(ds3$alcohol=="2"))/l3
  al3= length(which(ds3$alcohol=="3"))/l3
  al4 = length(which(ds3$alcohol=="4"))/l3
  al5 = length(which(ds3$alcohol=="5"))/l3
  
  sp1 = length(which(ds3$sport=="1"))/l4
  sp2 = length(which(ds3$sport=="2"))/l4

  cat("Smokers by Frequency\n ")
  cat("High Smokers: ")
  cat(hsm)
  cat("\n")
    cat("Low Smokers: ")
  cat(lsm)
  cat("\n")
    cat("Non Smokers: ")
  cat(nsm)
  cat("\n")
  
    cat("Frequency by Drug Consumption\n ")
  cat("High Users: ")
  cat(hd)
  cat("\n")
    cat("Occasional: ")
  cat(md)
  cat("\n")
    cat("Tried Once: ")
  cat(ld)
  cat("\n")
     cat("Non Users: ")
  cat(nd)
  cat("\n")
  
      cat("by Alcohol Consumption\n ")
  cat("High Users: ")
  cat(al5)
  cat("\n")
    cat("Occasional: ")
  cat(al4)
  cat("\n")
    cat("once a month: ")
  cat(al3)
  cat("\n")
     cat("once/twice a year: ")
  cat(al2)
  cat("\n")
  cat("Non Drinkers: ")
  cat(al1)
  cat("\n")
  
    cat("Sports by Frequency\n ")
  cat("High : ")
  cat(sp2)
  cat("\n")
    cat("Low : ")
  cat(sp1)
  cat("\n")
}
summary(ds3)
#(.72) who did not use cannabis or 72%
```
The proportion of students who do not use cannabis is 0.72
#e
```{r }
ds2$alcohol = factor(ds2$alcohol)
ds2$drugs = factor(ds2$drugs)
ds2$smoke = factor(ds2$smoke)
ds2$sport = factor(ds2$sport)
str(ds2)
class(ds2) <- c("s50survey")
summary(ds2)
temp = 50*(.74) - 50*(.38)
temp
```
People who played sports have decreased from 37 to 18

#q3 a
```{r }
ds1 <- import("HR021.csv",setclass = "tibble",header=TRUE)
colnames(ds1)

#colnames(ds1) = c("Sex","Admissions","CHO","`2015`","`2016`","`2017`")

str(ds1)


```

#q3 b
```{r }
library(dplyr)
tem = filter(ds1,ds1$Admissions=="All admissions",Sex == "Male")
tef = filter(ds1,ds1$Admissions=="All admissions",Sex == "Female")
t1 = sum(tem$`2017`)
t2 = sum(tef$`2017`)
t1
t2
```
The number of males : 8522
The number of females : 8478

#q3 c
```{r }
ds1new = filter(ds1,ds1$Admissions=="All admissions")
ds1new <- pivot_longer(ds1new, cols = `2015`:`2017`,
names_to = "Year", values_to = "`All admissions`")
dc = c('Admissions')
ds1new = ds1new[-2]

str(ds1new)

```


```{r }

ds1new = data.frame(ds1new)
ggplot(ds1new,aes(x=CHO,y=X.All.admissions.,color=Sex))+geom_point() + facet_wrap(~Year)

```
